### 2017-03-20 ResearchNotes/stat_exps.tex
Made minor corrections

The Profiling dataset contains a results field, however, the meaning of each
value in this field is unknown. So initially, this field is dropped. To get the
actual results of student we need the Results dataset.

@@

\begin{verbatim}
Two clusters
Conclusion: Clusters are found in users with different number of CRUD
activities. Silhouette score isn't that great
\end{verbatim}

@@

\subsection{\texttt{EXP\_005} - Predicting Students Grades From Course
Profiling}

>>>>

The Profiling dataset contains a results field, however, the meaning of each
value in this field is unknown. So initially, this field is dropped. To get the
actual results of students we need the Results dataset.

@@

This experiment isn't correct because there are nominal fields. Clustering may
be used in nominal fields, but the algorithms used in there may not.

@@

\subsection{\texttt{EXP\_005} - Predicting Students Grades From Student/Course
Profiling}
